{\bf {\Large Title....}}

### 2016-07-30 ident_manu.Rnw
ident tables added

source('R/funcs.r')
library(WRTDStidal)
library(tidyr)
library(ggplot2)
library(dplyr)
library(gridExtra)
library(Hmisc)
library(ggrepel)
library(english)
@

@@

Each of the three selection heuristics (blocked by parameter category, independent of category, all categories equally) for \ac{do} differed in the number of selected parameters and distribution of parameters within each category (if applicable, \cref{fig:heurist}).  For the first selection heuristic, all sensitive parameters from the optics ($n = $ \Sexpr{scinot(h1_id$Optics[[1]], digits = 0)}, $\gamma =$  \Sexpr{h1_id$Optics[[2]]}) and organic matter ($n = $ \Sexpr{scinot(h1_id$`Organic Matter`[[1]], digits = 0)}, $\gamma =$  \Sexpr{h1_id$`Organic Matter`[[2]]}) categories were selected, whereas \Sexpr{toeng(h1_id$Phytoplankton[[1]])[[1]]} were selected for phytoplankton ($\gamma = $ \Sexpr{h1_id$Phytoplankton[[2]]}), \Sexpr{toeng(h1_id$Temperature[[1]])[[1]]} for temperature ($\gamma = $ \Sexpr{h1_id$Temperature[[2]]}), and \Sexpr{toeng(h1_id$Zooplankton[[1]])[[1]]} for zooplankton ($\gamma = $ \Sexpr{h1_id$Zooplankton[[2]]}).  For the second selection heuristic, \Sexpr{toeng(h2_id[[1]])[[1]]} parameters were selected ($\gamma = $ \Sexpr{h2_id[[2]]}, with a majority from the phytoplankton category).  For the third heuristic, \Sexpr{toeng(h3_id[[1]])[[1]]} parameters were selected ($\gamma = $ \Sexpr{h3_id[[2]]}) with equal representation between categories. For the second and third selection heuristics, an individual parameter caused a disproportianate increase in $\gamma$ that forced the selection to stop.  Selection independent of category showed that including \Sexpr{par_txt(h2_brk[1])} caused in increase in $\gamma$ from \Sexpr{scinot(h2_brk[3], digits = 1)} to \Sexpr{scinot(h2_brk[2], digits = 1)} and equal selection within cateogies showed that including \Sexpr{par_txt(h3_brk[1])} caused in increase in $\gamma$ from \Sexpr{scinot(h3_brk[3], digits = 1)} to \Sexpr{scinot(h3_brk[2], digits = 1)}.  Finally, parameter selection for other state variables (\ac{chla}, \ac{par}, nitrate, ammonium, particulate organic matter, dissolved organic matter, phosphorus) also showed that a limited number of parameters were identifiable (for brevity, only results using the second set of selection heuristics are shown, \cref{fig:heurist_stts}).  Less than ten parameters were selected for each of the remaining state variables with most selected from the phytoplankton category.  Interestingly, no parameters from the temperature category were selected.

@@

% zooplankton sensitivity
<<zoopsens, eval = T, cache = F>>=
senstab2('Zooplankton', 'zoopsens')
@
\clearpage

@@

% heuristic plots o2
<<heurist, fig.cap = 'Identifiability (as $\\gamma$, \\cref{gameq}) of selecting parameters with three different heuristics. Parameters are selected by decreasing sensitivity for all examples (\\cref{tab:optsens,tab:tempsens,tab:phytosens,tab:zoopsens,tab:omsens}). The parameter selecions are blocked within each category (a), independent of category (b), or considering all categories equally (c). Grey lines indicate potential thresholds at $\\gamma = 10, 15$ for maximum acceptable identifiability. Selection stops after $\\gamma > 15$ or if the maximum number of possible parameters is selected.', fig.height = 8, fig.width = 8, echo = F, cache = TRUE, out.width = '\\textwidth'>>=

@@

% heuristic plots, all state
<<heurist_stts, fig.cap = 'Identifiability (as $\\gamma$, \\cref{gameq}) of selecting parameters for selected state variables. Parameters are selected by decreasing sensitivity indepent of parameter categories. Grey lines indicate potential thresholds at $\\gamma = 10, 15$ for maximum acceptable identifiability. Selection stops after $\\gamma > 15$.', fig.height = 5, fig.width = 9, echo = F, cache = TRUE, out.width = '\\textwidth'>>=
data(tocal_all)

>>>>

source('R/funcs.r')
library(WRTDStidal)
library(tidyr)
library(ggplot2)
library(dplyr)
library(gridExtra)
library(Hmisc)
library(ggrepel)
library(english)
library(purrr)
@

@@

Each of the three selection heuristics (blocked by parameter category, independent of category, all categories equally) for \ac{do} differed in the number of selected parameters and distribution of parameters within each category (if applicable, \cref{fig:heurist,tab:identall1}).  For the first selection heuristic, all sensitive parameters from the optics ($n = $ \Sexpr{scinot(h1_id$Optics[[1]], digits = 0)}, $\gamma =$  \Sexpr{h1_id$Optics[[2]]}) and organic matter ($n = $ \Sexpr{scinot(h1_id$`Organic Matter`[[1]], digits = 0)}, $\gamma =$  \Sexpr{h1_id$`Organic Matter`[[2]]}) categories were selected, whereas \Sexpr{toeng(h1_id$Phytoplankton[[1]])[[1]]} were selected for phytoplankton ($\gamma = $ \Sexpr{h1_id$Phytoplankton[[2]]}), \Sexpr{toeng(h1_id$Temperature[[1]])[[1]]} for temperature ($\gamma = $ \Sexpr{h1_id$Temperature[[2]]}), and \Sexpr{toeng(h1_id$Zooplankton[[1]])[[1]]} for zooplankton ($\gamma = $ \Sexpr{h1_id$Zooplankton[[2]]}).  For the second selection heuristic, \Sexpr{toeng(h2_id[[1]])[[1]]} parameters were selected ($\gamma = $ \Sexpr{h2_id[[2]]}, with a majority from the phytoplankton category, \cref{tab:identall1}).  For the third heuristic, \Sexpr{toeng(h3_id[[1]])[[1]]} parameters were selected ($\gamma = $ \Sexpr{h3_id[[2]]}) with equal representation between categories. For the second and third selection heuristics, an individual parameter caused a disproportianate increase in $\gamma$ that forced the selection to stop.  Selection independent of category showed that including \Sexpr{par_txt(h2_brk[1])} caused in increase in $\gamma$ from \Sexpr{scinot(h2_brk[3], digits = 1)} to \Sexpr{scinot(h2_brk[2], digits = 1)} and equal selection within cateogies showed that including \Sexpr{par_txt(h3_brk[1])} caused in increase in $\gamma$ from \Sexpr{scinot(h3_brk[3], digits = 1)} to \Sexpr{scinot(h3_brk[2], digits = 1)}.  Finally, parameter selection for other state variables (\ac{chla}, \ac{par}, nitrate, ammonium, particulate organic matter, dissolved organic matter, phosphorus) also showed that a limited number of parameters were identifiable (for brevity, only results using the second set of selection heuristics are shown, \cref{fig:heurist_stts,tab:identall2}).  Less than ten parameters were selected for each of the remaining state variables with most selected from the phytoplankton category.  Interestingly, no parameters from the temperature category were selected.

@@

% zooplankton sensitivity
<<zoopsens, eval = T, cache = F>>=
senstab2('Zooplankton', 'zoopsens')
@

% ident all states
<<identdo, eval = T, cache = F>>=
data(tocal_all)

# factor levels
cats_lev <- c('Optics', 'Organic Matter', 'Phytoplankton', 'Temperature', 'Zooplankton')
cats_lab <- c('O', 'OM', 'P', 'T', 'Z')
stts_lev <- rev(c('NH4', 'Chla_mg_tot', 'O2', 'irradiance', 'NO3', 'OM1', 'OM2', 'PO4'))
stts_lab <- rev(c('Ammonium', 'Chlorophyll', 'Dissolved Oxygen', 'Irradiance', 'Nitrate', 'OM1', 'OM2', 'Phosphate'))

labs <- parcats2(as_df = T) %>% 
    rename(Parameter = shrt) %>% 
    select(Parameter, lngs)

# format tocal_all for identifiability table
# add long parameter name
# get parameter combos with coll < 15 + 1
# format error and coll with scinot
# format category label so no duplicates
totab <- tocal_all$top_all %>% 
  reshape2::melt(., id.var = names(.[[1]])) %>%
  mutate(Parameter = as.character(Parameter)) %>% 
  left_join(., labs, by = 'Parameter') %>% 
  mutate(
    lngs = gsub('^[a-z,A-Z,0-9]*:\\s', '', lngs), 
    lngs = gsub('_', '', lngs), 
    stts = factor(L1, levels = stts_lev, labels = stts_lab),
    Category = factor(Category, levels = cats_lev, labels = cats_lab), 
    Parameter = par_txt(Parameter, frm = 'tex')
  ) %>% 
  split(., .$L1) %>% 
  lapply(function(x){

    sel <- which(x$coll < 15)
    x <- x[sel, ] %>% 
    # x <- x[c(sel, max(sel) + 1), ] %>% 
      na.omit
    x

  }) %>% 
  do.call('rbind', .) %>%
  mutate(
    error = sapply(error, scinot),
    coll = sapply(coll, scinot), 
    Rank = sapply(rnk_incat, scinot), 
    Rank = paste0(Rank, '\\textsuperscript{', Category, '}')
    ) %>%
  group_by(stts) %>% 
  nest %>% 
  unnest %>% 
  select(stts, lngs, Parameter, Rank, error, coll) %>% 
  rename(
    Description = lngs, 
    L1 = error
  ) %>% 
  mutate(
    stts = as.character(stts),
    Description = paste0('\\scriptsize{', Description, '}'),
    Parameter = paste0('\\scriptsize{', Parameter, '}')
    ) %>% 
  arrange(stts)

identall1 <- filter(totab, stts %in% 'Dissolved Oxygen')

# final table formatting
descrip <- as.character(identall1$Description)
identall1 <- identall1[,-c(1, 2)]
cap_val<- 'Parameter identifiability for dissolved oxygen.  Selection followed the second heuristic where parameters were selected by decreasing sensitivity up to maximum $\\gamma < 15$.  Rank describes the parameter sensitivity in each category (O: optics, OM: organic matter, P: phytoplankton, T: temperature, Z: zooplankton).'
colnms <- c('Parameter', 'Rank', 'L1', '$\\gamma$')

latex( 
  identall1,
  file = '',
  rowlabel = 'Parameter description',
  caption = cap_val,
  caption.loc = 'top',
  size = 'footnotesize',
  label = 'tab:identall1',
  rowname = descrip,
  colheads = colnms,
  rgroupTexCmd = NULL
  )
@

% ident all states
<<identall, eval = T, cache = F>>=
data(tocal_all)

# factor levels
cats_lev <- c('Optics', 'Organic Matter', 'Phytoplankton', 'Temperature', 'Zooplankton')
cats_lab <- c('O', 'OM', 'P', 'T', 'Z')
stts_lev <- rev(c('NH4', 'Chla_mg_tot', 'O2', 'irradiance', 'NO3', 'OM1', 'OM2', 'PO4'))
stts_lab <- rev(c('Ammonium', 'Chlorophyll', 'Dissolved Oxygen', 'Irradiance', 'Nitrate', 'OM1', 'OM2', 'Phosphate'))

labs <- parcats2(as_df = T) %>% 
    rename(Parameter = shrt) %>% 
    select(Parameter, lngs)

# format tocal_all for identifiability table
# add long parameter name
# get parameter combos with coll < 15 + 1
# format error and coll with scinot
# format category label so no duplicates
totab <- tocal_all$top_all %>% 
  reshape2::melt(., id.var = names(.[[1]])) %>%
  mutate(Parameter = as.character(Parameter)) %>% 
  left_join(., labs, by = 'Parameter') %>% 
  mutate(
    lngs = gsub('^[a-z,A-Z,0-9]*:\\s', '', lngs), 
    lngs = gsub('_', '', lngs), 
    stts = factor(L1, levels = stts_lev, labels = stts_lab),
    Category = factor(Category, levels = cats_lev, labels = cats_lab), 
    Parameter = par_txt(Parameter, frm = 'tex')
  ) %>% 
  split(., .$L1) %>% 
  lapply(function(x){

    sel <- which(x$coll < 15)
    x <- x[sel, ] %>% 
    # x <- x[c(sel, max(sel) + 1), ] %>% 
      na.omit
    x

  }) %>% 
  do.call('rbind', .) %>%
  mutate(
    error = sapply(error, scinot),
    coll = sapply(coll, scinot), 
    Rank = sapply(rnk_incat, scinot), 
    Rank = paste0(Rank, '\\textsuperscript{', Category, '}')
    ) %>%
  group_by(stts) %>% 
  nest %>% 
  unnest %>% 
  select(stts, lngs, Parameter, Rank, error, coll) %>% 
  rename(
    Description = lngs, 
    L1 = error
  ) %>% 
  mutate(
    stts = as.character(stts),
    Description = paste0('\\scriptsize{', Description, '}'),
    Parameter = paste0('\\scriptsize{', Parameter, '}')
    ) %>% 
  arrange(stts)

identall2 <- filter(totab, !stts %in% 'Dissolved Oxygen')

# final table formatting
stts <- identall2$stts
descrip <- as.character(identall2$Description)
identall2 <- identall2[,-c(1, 2)]
cap_val<- 'Parameter identifiability for ammonium, chlorophyll, irradiance, nitrate, OM1, OM2, and phosphate.  Selection followed the second heuristic where parameters were selected by decreasing sensitivity up to maximum $\\gamma < 15$.  Rank describes the parameter sensitivity in each category (O: optics, OM: organic matter, P: phytoplankton, T: temperature, Z: zooplankton).'
colnms <- c('Parameter', 'Rank', 'L1', '$\\gamma$')

latex( 
  identall2,
  file = '',
  rowlabel = 'State variable, parameter description',
  caption = cap_val,
  caption.loc = 'top',
  size = 'footnotesize',
  label = 'tab:identall2',
  rgroup = unique(as.character(stts)),
  n.rgroup = as.numeric(table(as.character(stts))),
  rowname = descrip,
  colheads = colnms,
  rgroupTexCmd = NULL
  )
@
\clearpage

@@

% heuristic plots o2
<<heurist, fig.cap = 'Identifiability (as $\\gamma$, \\cref{gameq}) of selecting parameters with three different heuristics. Parameters are selected by decreasing sensitivity for all examples (\\cref{tab:optsens,tab:tempsens,tab:phytosens,tab:zoopsens,tab:omsens}). The parameter selecions are blocked within each category (a), independent of category (b), or considering all categories equally (c). Grey lines indicate potential thresholds at $\\gamma = 10, 15$ for maximum acceptable identifiability. Selection stops after $\\gamma > 15$ or if the maximum number of possible parameters is selected. See \\cref{tab:identall1} for values in (b).', fig.height = 8, fig.width = 8, echo = F, cache = TRUE, out.width = '\\textwidth'>>=

@@

% heuristic plots, all state
<<heurist_stts, fig.cap = 'Identifiability (as $\\gamma$, \\cref{gameq}) of selecting parameters for selected state variables. Parameters are selected by decreasing sensitivity indepent of parameter categories. Grey lines indicate potential thresholds at $\\gamma = 10, 15$ for maximum acceptable identifiability. Selection stops after $\\gamma > 15$.  See \\cref{tab:identall2} for values.', fig.height = 5, fig.width = 9, echo = F, cache = TRUE, out.width = '\\textwidth'>>=
data(tocal_all)
